 
 \subsection{Contributors}
 
  This document is the result of the joint efforts of many
  contributors. The authors listed here and on the title page are
  those taking responsibility for the content of the document, and all
  errors. The editors (underlined) are committed to taking permanent
  stewardship for this document and can be contacted in the future for
  inquiries.
 
 
 \begin{center}
  \begin{tabular}{ll}
   \B{Tom Goodale}                    & \B{\U{Shantenu Jha}}      \\
   \T{t.r.goodale@cs.cardiff.ac.uk}   & \T{s.jha@ucl.ac.uk}       \\
   Cardiff School of Computer Science & Center for Computational 
                                        Science                   \\
   5, The Parade, Roath               & University College London \\
   Cardiff, CF24 3AA                  & London, WC1H 0AJ          \\
   United Kingdom                     & United Kingdom            \\
                                                                  \\ 
   \B{Hartmut Kaiser}                 & \B{\U{Thilo Kielmann}}    \\
   \T{hkaiser@cct.lsu.edu}            & \T{kielmann@cs.vu.nl}     \\
   Center for Computation and 
   Technology                         & Vrije Universiteit        \\
   Louisiana State University         & Dept.~of Computer Science \\
   216 Johnston Hall                  & De Boelelaan 1083         \\
   70803 Baton Rouge                  & 1081HV Amsterdam          \\
   Louisiana, USA                     & The Netherlands           \\
                                                                  \\ 
   \B{Pascal Kleijer}                 & \B{\U{Andre Merzky}}      \\
   \T{k-pasukaru@ap.jp.nec.com}       & \T{andre@merzky.net}      \\
   NEC Corporation                    & VU (see Kielmann)         \\
   HPC Marketing Promotion            & CCT/LSU (see Kaiser)      \\
   1-10, Nisshin-cho, Fuchu           &                           \\
   183-8501 Tokyo                     &                           \\
   Japan                              &                           \\
                                      &                           \\
                                                                  \\
   \B{John Shalf}                     & \B{Christopher Smith}     \\
   \T{jshalf@lbl.gov}                 & \T{csmith@platform.com}   \\
   Lawrence Berkeley                  & Platform Computing Inc.   \\
   National Laboratory                & USA                       \\
   Mailstop 50F                       &                           \\
   1 Cyclotron Road                   &                           \\
   94720 Berkeley                     &                           \\
   California, USA                    &                           \\
  \end{tabular}
 \end{center}
 
 
  The initial version of the presented SAGA API was drafted by the
  SAGA Design Team.  Members of that design team did not
  necessarily contribute text to the document, but did certainly
  contribute to its current state, and very much so.  Additional
  to the authors listed above, the following people were members
  of the design team, in alphabetical order:
   
  Hrabri Rajic (Intel),
  Keith Jackson (LBL),
  David Konerding (LBL),
  Gregor von Laszewski (ANL).
   
  Further, the authors would like to thank all contributors from
  OGF's SAGA-RG and SAGA-CORE-WG, and other related groups.  We
  would like to acknowledge, in alphabetical order, the
  contributions of:
   
  Gabrielle Allen (LSU),
  Stephan Hirmer (LSU),
  Craig Lee (Aerospace Corporation),
  Hidemoto Nakada (AIST),
  Steven Newhouse (OMII-UK),
  Stephen Pickles (University of Manchester),
  Ed Seidel (LSU),
  Derek Simmel (PSC),
  Yusuke Tanimura (AIST),
  Osamu Tatebe (University of Tsukuba).
   
  % please add others !!!
 
 
 
 \subsection{Intellectual Property Statement}
 
  The OGF takes no position regarding the validity or scope of any
  intellectual property or other rights that might be claimed to
  pertain to the implementation or use of the technology described in
  this document or the extent to which any license under such rights
  might or might not be available; neither does it represent that it
  has made any effort to identify any such rights. Copies of claims of
  rights made available for publication and any assurances of licenses
  to be made available, or the result of an attempt made to obtain a
  general license or permission for the use of such proprietary rights
  by implementers or users of this specification can be obtained from
  the OGF Secretariat. 

  The OGF invites any interested party to bring to its attention any
  copyrights, patents or patent applications, or other proprietary
  rights which may cover technology that may be required to practice
  this recommendation. Please address the information to the OGF
  Executive Director.
 
 
 \subsection{Disclaimer}
 
  This document and the information contained herein is provided on an
  ``As Is'' basis and the OGF disclaims all warranties, express or
  implied, including but not limited to any warranty that the use of
  the information herein will not infringe any rights or any implied
  warranties of merchantability or fitness for a particular purpose. 
  
 
 \subsection{Full Copyright Notice}
 
  Copyright (C) Open Grid Forum (2006). All Rights Reserved. 
 
  This document and translations of it may be copied and furnished to
  others, and derivative works that comment on or otherwise explain it
  or assist in its implementation may be prepared, copied, published
  and distributed, in whole or in part, without restriction of any
  kind, provided that the above copyright notice and this paragraph
  are included on all such copies and derivative works.  However, this
  document itself may not be modified in any way, such as by removing
  the copyright notice or references to the OGF or other
  organizations, except as needed for the purpose of developing Grid
  Recommendations in which case the procedures for copyrights defined
  in the OGF Document process must be followed, or as required to
  translate it into languages other than English. 

  The limited permissions granted above are perpetual and will not be
  revoked by the OGF or its successors or assignees. 
 
